Modalities for Location Virtualization

### 2022-09-20 cpp_paper.tex
separted stuff
+
stuff from colin
some intro stuff, bibliography
../..
write most of related work
try and fail to make the listings non-hideous
marginally less ugly assembly listings

\documentclass[sigplan,10pt,anonymous,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

\maketitle
\input{intro.tex}
\input{background.tex}
\input{syntax.tex}
\input{semantics.tex}
\input{programlogic.tex}
\input{examples.tex}
\input{discussion.tex}
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

>>>>

\documentclass[sigplan,10pt,anonymous,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage[utf8]{inputenc}
\usepackage{todonotes}
\usepackage{blindtext}
\usepackage{listings}
\lstset{
  columns=fullflexible,
  numbers=left,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue}\bfseries,
  morekeywords={mov,add,call},
  emph={rdx,rax,rbx,rbp,rsi,rdi,rcx,r8,r9,r10,r11,r12,r13,r14,r15},
  emphstyle=\color{green},
  emph={[2]cr3},
  emphstyle={[2]\color{violet}},
  morecomment=[l]{;;}
}
% Hack for Colin to edit in low light: https://tex.stackexchange.com/questions/40495/invert-background-and-text-colours-across-whole-document-with-pdflatex
%Commands definitions
\newcommand{\setbackgroundcolour}{\pagecolor[rgb]{0.19,0.19,0.19}}  
\newcommand{\settextcolour}{\color[rgb]{0.77,0.77,0.77}}    
\newcommand{\invertbackgroundtext}{\setbackgroundcolour\settextcolour}
%Command execution. 
%If this line is commented, then the appearance remains as usual.
\invertbackgroundtext

% Packages.
\usepackage{amsmath}
% If we need multiple references to a footnote, via \cref:
\usepackage{cleveref}
\crefformat{footnote}{#2\footnotemark[#1]#3}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage{iris}
\usepackage{mathpartir}
\renewcommand{\TirNameStyle}[1]{\hypertarget{#1}{\textsc{#1}}}
\newcommand{\RULE}[1]{\hyperlink{#1}{\textsc{#1}}\xspace}
\usepackage{xspace}
\input{macros}

\newcommand{\mytodo}[1]{% <==========================================
  \todo[linecolor=white, bordercolor=white, textcolor=white]{#1}%
}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{program verification}

\maketitle

{
\theoremstyle{acmdefinition}
\newtheorem{assumption}[theorem]{Assumption}
}

\input{intro.tex}
%\input{motivation.tex}
\input{background.tex}
\input{syntax.tex}
\input{semantics.tex}
\input{programlogic.tex}
\input{soundness.tex}
\input{examples.tex}
\input{discussion.tex}
\input{relwork.tex}
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{vmm}
